R Notebook

### 2022-08-31 hw1-1/abhinav/knn.Rmd
Final KNN model updated

```{r}
#imports
library(kknn)
```

```{r}
knn_data<-read.table("./hw1-1/data 2.2/credit_card_data-headers.txt",sep='\t',header=TRUE)
dim(knn_data)
```

@@

```{r}
#anshit to review from here -> loop over k and get a dataframe with k,threshold and auc value, accuracies
k0=21
test_pred<-data.frame(pred_val=double(0),act_class=numeric(0))
for (i in 1:nrow(knn_data)){
    knn_model_v1<-kknn(R1~.,train = knn_data[-i,],test = knn_data[i,],k=k0,kernel="rectangular",scale = TRUE)
    knn_pred[i]<-as.double(fitted(knn_model_v1))
    test_pred[nrow(test_pred)+1,]=c(knn_pred[i],knn_data$R1[i])
}
```

```{r}
accuracy_knn <- function(df){
  acc_overall = sum(df$act_class == df$pred_class)/nrow(df)
  df_1 = df[df$act_class > 0,]
  df_0 = df[df$act_class == 0,]
  acc_1 = sum(df_1$act_class == df_1$pred_class)/nrow(df_1)
  acc_0 = sum(df_0$act_class == df_0$pred_class)/nrow(df_0)
  return (c(acc_overall, acc_1, acc_0))
}
```

```{r}
threshold_auc<-data.frame(threshold_val=double(0),auc_val=double(0),acc_overall=double(0),acc_1=double(0),acc_0=double(0))
for(t0 in seq(0.2,0.8,by=0.02)){
  f0<-function(x,t=t0){
    ifelse(x>t,1,0)
  }
  test_pred$pred_class<-apply(data.frame(test_pred$pred_val),1,f0)
  # function to get overall , 0's and 1's accuracy
  # accuracy_knn(test_pred)
  auc_val<-auc(test_pred$act_class,test_pred$pred_class)
  threshold_auc[nrow(threshold_auc)+1,]=c(t0,auc_val,accuracy_knn(test_pred))
}
```

```{r}
head(threshold_auc)
accuracy_knn(test_pred)
```

```{r}
#roc_score=roc(test_pred$act_class,test_pred$pred_class)
#plot(roc_score ,main ="ROC curve --KNN ")
print(paste("Max AUC score :" ,round(max(threshold_auc$auc_val),2)))
print(paste("Threshold values for which max AUC score is attained", threshold_auc$threshold_val[threshold_auc$auc_val==max(threshold_auc$auc_val,na.rm=TRUE)]))
```

>>>>

```{r}
#imports
library(kknn)
library(pROC)
```

```{r}
knn_data<-read.table("../data 2.2/credit_card_data-headers.txt",sep='\t',header=TRUE)
dim(knn_data)
```

@@

```{r}
# Accuracy Function
accuracy_knn <- function(df){
  acc_overall = sum(df$act_class == df$pred_class)/nrow(df)
  df_1 = df[df$act_class > 0,]
  df_0 = df[df$act_class == 0,]
  acc_1 = sum(df_1$act_class == df_1$pred_class)/nrow(df_1)
  acc_0 = sum(df_0$act_class == df_0$pred_class)/nrow(df_0)
  return (c(acc_overall, acc_1, acc_0))
}
```

```{r}
# Threshold Function
f0<-function(x,t=t0){
  ifelse(x>t,1,0)
}
```

```{r}
# Data frame for storing values
threshold_auc<-data.frame(k=double(0), threshold_val=double(0), auc_val=double(0), acc_overall=double(0), acc_1=double(0), acc_0=double(0))

# Loop iterating over values of K for findind best value of K
for(k in seq(20, 50, by=5)){
  test_pred<-data.frame(pred_val=double(0),act_class=numeric(0))
  for (i in 1:nrow(knn_data)){
      knn_model_v1<-kknn(R1~., train = knn_data[-i,], test = knn_data[i,], k=k, kernel="rectangular", scale = TRUE)
      knn_pred[i]<-as.double(fitted(knn_model_v1))
      test_pred[nrow(test_pred)+1,]=c(knn_pred[i],knn_data$R1[i])
  }

  # Iterating over values of threshold to determine the threshold which maximizes AUC score and hence the better separation between the two classes
  for(t0 in seq(0.2,0.8,by=0.02)){
    test_pred$pred_class<-apply(data.frame(test_pred$pred_val),1,f0)
    auc_val<-auc(test_pred$act_class,test_pred$pred_class)
    print(auc_val)
    print(c(k, t0, auc_val, accuracy_knn(test_pred)))
    threshold_auc[nrow(threshold_auc)+1,]=c(k, t0,auc_val,accuracy_knn(test_pred)[1], accuracy_knn(test_pred)[2], accuracy_knn(test_pred)[3])
  }
}
```

```{r}
threshold_auc
```

```{r}
# Final step to determine the highest value of AUC for every K
final_frame<-data.frame(k=double(0), threshold_val=double(0), auc_val=double(0), acc_overall=double(0), acc_1=double(0), acc_0=double(0))
for(k_i in seq(20, 50, by=5)){
  print(k_i)
  data_i = threshold_auc[threshold_auc$k == k_i,]
  print (data_i[which.max(data_i$auc_val),])
  final_frame[nrow(final_frame)+1] = c(data_i[which.max(data_i$auc_val),])
}
```

```{r}
final_frame
```
